Transparency of COVID-19-related research - Analysis

### 2022-04-21 rmarkdown-covid-19-transparent-analysis.Rmd

```{r}
pacman::p_load(tidyverse,
               lubridate, 
               here, 
               ggplot2,
               knitr,
               here)
```

# Loading the datasets
First, set working directory to the folder that has all the datasets in it using setwd() function and then run the following code:
```{r}
opendata <- read.csv(here("data", "covid_transparency_opendata.csv"))
```

>>>>

```{r}
pacman::p_load(tidyverse,
               lubridate, 
               here, 
               ggplot2,
               knitr,
               here,
               epiR,
               ggpubr,
               tibble)
```

# Loading the datasets

```{r}
opendata <- read.csv(here("data", "covid_transparency_opendata.csv"))
```
